Supporting Information

### 2021-10-28 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
new update
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 1), ncol = 1, nrow = 3)

dev.new()
png("q1_2_new.png", width = 1400, height = 2200)
p7
graphics.off()

@@

p8 <- p8 + 
  ggplot2::ggtitle("Question 2.1") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 16, face = "bold"))

dev.new()
png("q2_new.png", width = 1000, height = 350)
p8
graphics.off()

>>>>

p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 0.7), ncol = 1, nrow = 3)

dev.new()
png("q1_2_new.png", width = 1000, height = 2500)
p7
graphics.off()

@@

p8 <- p8 + 
  ggplot2::ggtitle("Question 2.1") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 20, face = "bold"))

dev.new()
png("q2_new.png", width = 1000, height = 500)
p8
graphics.off()
